---
title: "Example Rmd report"
author: "Joseph and Faith"
output: html_document
theme: cosmo
---
## Heading number 1 -download file and read into R
Here we are using the 'download.file()' command to obtain the dataset
then we are reading it into R. It is important to set 'header=TRUE'
and 'row.nmaes=1' so that the data is formated properly

```{r,chunk1,echo=TRUE}
# Download the data
download.file("https://raw.githubusercontent.com/markziemann/SLE712_files/master/bioinfo_asst3_part1_files/mydata.tsv",destfile = "mydata.tsv")

#Read table into R making sure the 1st column is set as row names and headers recognized
x <- read.table("mydata.tsv", header = TRUE, row.names = 1,stringsAsFactors = FALSE)
```

## Heading 2 -checking data integrity
Here we use 'head ()' and  to look at the first 6lines of the data frame
and the 'str ()'to make sure the contents are recognized as numeric.

```{r,chunk2,echo=TRUE}
# check if the data  has been imported properly
head(x)

# checking for data structure
str(x)
```
